A Hedonic Price Analysis of Traffic Noise in the Twin Cities Housing Market

### 2013-08-29 reports/Draft.Rnw

An important first step towards such an analysis is to examine real estate price fluctuations as a function of noise levels using hedonic regression.  Such work has provided important insight on the nature of this relationship.  Thus, Bateman et al. (2001) found that the negative eﬀect of traﬃc noise ranged from 0.08\% to 2.22\% per dB with a mean around 0.55\% per dB. In a review of 65 noise evaluation studies Navrud (2002) found an average decrease of 0.64\% per dB. \textbf{We need to briefly review other relevant papers here.}  However, with the exception of a few studies that have focused on air traffic noise exposure (we should check on this), the relationship between road traffic noise levels and real estate prices has rarely been explored in the United States, even though the former is perhaps the greatest source of noise in residential neighborhoods (XXX).  One major reason for the thinness of the scholarly literature on this topic in the US lies in the difficulty of modeling noise propagation over the landscape.

>>>>

An important first step towards such an analysis is to examine real estate price fluctuations as a function of noise levels using hedonic regression.  Such work has provided important insight on the nature of this relationship.  Thus, \citet{Bateman2001} found that the negative eﬀect of traﬃc noise ranged from 0.08 to 2.22 percent per dB with a mean around 0.55 percent per dB. In a review of 65 noise evaluation studies \citet{Navrud2002} found an average decrease of 0.64 percent per dB. \textbf{We need to briefly review other relevant papers here.}  However, with the exception of a few studies that have focused on air traffic noise exposure \textbf{(see, for instance, \citet{coh})}, the relationship between road traffic noise levels and real estate prices has rarely been explored in the United States, even though the former is perhaps the greatest source of noise in residential neighborhoods (XXX).  One major reason for the thinness of the scholarly literature on this topic in the US lies in the difficulty of modeling noise propagation over the landscape.  
>>>>>>> 4543f31da98e1080a1ead85b6607230c99f3c848
